Draft

### 2020-03-11 Draft.Rmd
update

# Introduction
The improved theoretical understanding in AI technology, the ubiquity of large annotated datasets, and the advance in computer power have fostered a rapid expansion of the AI industry in medical diagnosis.

Until recently, the most accurate AI methods for image analysis involved painstaking feature engineering, which requires manual image pre-processing, segmenting anatomic structures, and detecting or computing features suggested by an expert. The breakthrough in the ImageNet 2012 Challenges popularized the use of deep learning in neural networks to analyse medical images. Inspired by the human nervous system, neural networks are interconnected functions, each comprised of a weight and a bias coefficient. In deep learning, the networks are trained using large sets of known positive and negative data (ground truth) in multiple hidden layers. The networks “learn” by adjusting the weights and biases of the underlying functions based on the difference between predictions and ground, a process called back-propagation. The increased computational power makes it possible for a complex deep learning network to modify itself using a large training dataset so that the resulting trained algorithms can identify new and unseen data.

@@

# Methods
With funding from the Stop TB Partnership’s TB REACH initiative, three TB Screening Centres (SCs) were established across Dhaka with a referral network of more than 2,000 private providers and 133 NTP facilities. Health providers in the network refer presumptive TB patients to the SCs to screen and test for TB. Public health facilities only refer the people with a negative smear microscopy but still suspected of having TB to the SCs. The TB SCs also receive walk-in clients with no referral history.

We consecutively enrolled all adults (> 15 years) presenting at any of the TB SCs between 15 May 2014 and 4 October 2016. After providing informed consent, each participant was verbally screened for symptoms and received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test. Xpert test was performed again if the initial test failed (invalid, error, or no result). The final Xpert results were used as the bacteriological evidence and the refernece standard in this evaluation. A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely. The radiologists were blinded to all testing and clinical (and demographic data?? icddr,b please confirm) data and provided standard radiology reports and graded each CXR as follows (criteria to be attached): a. Highly Suggestive: including highly suggestive of TB only, b. Possibly TB: including abnormality highly suggestive of TB and possibly associated with TB, c. Any Abnormality: including abnormality highly suggestive of TB, possibly associated with TB and non-TB abnormality, d. Normal. Anyone who was unable or unwilling to acquire a CXR was referred to a nearby public-sector health facility.

Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems with stable version control to be included included in this study: CAD4TB (version 6), qXR (version 1) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (Version 4.7.2) developed by Lunit (South Korea), JF CXR-1 developed by JF Healthcare (China) and InferRead®DR by Infervision version 2 (China).We used the latest versions available of the five DL systems in this evaluation. Current versions of qXR and Lunit detect several discrete pulmonary abnormalities, such as calcification, cavitation, opacities etc. (to be updated with landscaping results). All five DL systems can generate heat maps showing abnormalities. The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer. All machine reading was performed independently with the developers blinded to all testing, clinical and demographic data.

All DL systems produce a continuous score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB based on their DL algorithms. We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB. Mann-Whitney U test was used to compared non-normal distribution. Some vendors provide binary (“Yes” / “No”) for TB using a pre-defined threshold score. We choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below). For example, for highly suggestive of TB, we chose the cutoff score to produce the same dichotomized screening decisions in terms of sensitivity and we compare the difference in specificity using McNemar test for paired proportions.

@@

A total of `r  length(MDF$X)` people were consecutively recruited from the three TB SCs. Excluding `r sum(is.na(MDF$rad.abn)==T)` individuals without a CXR and `r sum(MDF$Age<15)` individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis. The median age was `r T1$Overall[2]`, and the ratio between female and male participants was `r T1$Overall[3]`. Most participants `r T1$Overall[4]`,  reported coughing more than 14 days (or any cough? icddr,b please check), `r T1$Overall[5]` reported fever, `r T1$Overall[7]` reported weight loss; about half reported shortness of breath `r T1$Overall[6]`; `r  T1$Overall[8]` reported hemoptysis; and `r T1$Overall[10]` had prior TB medication history. Almost all, `r T1$Overall[9]` had at least one TB-related symptom. There are three sources of patients: the greatest proportion of test results came from people who were referred by their private provider (n=`r T1$Overall[24]`);  `r T1$Overall[25]` were referred from NTP facilities after a negative smear; and `r T1$Overall[26]` individuals walked-in / self-presented (Table 1).

Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]` compared with `r T1$Private[11]` and `r T1$Public[11]` for other referral groups. Among people with MTB-positive results, `r percent(sum(MDF$RIF.Result %in% "Detected")/sum(MDF$Xpert2Outcome_num %in% "1"))` were resistant to rifampicin. The radiologists graded `r T1$Overall[27]` as Highly Suggestive, `r T1$Overall[28]` as Possibly TB, `r T1$Overall[29]` as Any Abnormality. The medians of the abnormality scores in Xpert positive groups were significantly different from those in the Xpert negative groups were (Mann-Whitney U test <0.05) for all 5 DL systems.

### Histogram

![](Results/Histogram.tif){width=900px}

The distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and prior TB history (Figure 1) were distinct, suggesting the algorithms are constructed differently. In terms of the segregation of Xpert positive and negative individuals, JF CXR-1's scores of Xpert positive were heavily left-skewed (skewness = `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 31]),3)`, the green bars in Figure 1); whereas the Xpert positive individuals' CAD4TB scores were lest left skewed (skewness= `r round(skewness(MDF[MDF$Xpert2Outcome_num ==1, 27]),3)`), but still almost all above 50%. There were some noticeable outliers in the Xpert positive group whose AI scores were unexpectedly low, which represents true positive patients being missed or reduced sensitivity.

There were many Xpert negative individuals have relatively high probablity scores. Noticeably some unexpectively had very high score (90-100) when read by JF CXR-1. 
As expected the distributions in Xpert negative group were right-skewed except for CAD4TB with a left skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 27]),4)`, and Infervision has the highest right skewness of `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0, 33]),3)`.

Noticeably, there are many distinct outliers: the far right side of the JF CXR-1's distribution in the Xpert negative group (score 90-100) and qXR in the Xpert negative group (score 70-90), far left sides of Lunit's and JF CXR-1's distribution in the Xpert negative group (score 0-10). Those with TB history but Xpert negative without in generally still have a high AI scores, especially in the case of JF CXR-I (the dark red bar), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarring and active lesion.

### Comparison of sensitivity and specificity between human reading and the predictions of the DL systems
```{r}
source("radiologist.R")
humanAI <- read.csv("Results/HumanAI.csv", )
humanAI <- humanAI[c(3,6,9,12,15, 2,5,8,11,14, 1,4,7,10,13), -c(7, 9, 10)]

knitr::kable(humanAI, row.names = F)
```

Thresholds were chosen to match or exceed the performance of each human reader’s categories.

If all patients with a chest x-ray graded as highly suggestive of TB by the radiologists had been tested by Xpert, the resulting sensitivity and specificity would be `r paste0(percent(Radiologist$Sens[1]), ", 95CI: (", percent(Radiologist$Sens_L[1]), " - ", percent(Radiologist$Sens_H[1]),")")` and `r paste0(percent(Radiologist$Spec[1]), ", 95CI: (", percent(Radiologist$Spec_L[1]), " - ", percent(Radiologist$Spec_H[1]),")")`. When approximate the sensitivity of this classification made by human readers, all 5 DL systems demonstrated statistically significant improvement in specificity (improvement ranging from 1.48% - 8.96%).

If radiologists' rading of "Possibly TB" had been used to triage the follow-on Xpert testing, the resulting sensitivity would be `r paste0(percent(Radiologist$Sens[2]), ", 95CI: (", percent(Radiologist$Sens_L[2]), " - ", percent(Radiologist$Sens_H[2]), ")")` and the specificity would be `r paste0(percent(Radiologist$Spec[2]), ", 95CI: (", percent(Radiologist$Spec_L[2]), " - ", percent(Radiologist$Spec_H[2]), ")")`. The matching AI classificiation by the 5 DL systems showed statistical improvement in specificty (improvement ranging from 1.34% - 7.62%).

The grading of Possibly TB" would have a sensitivity of `r paste0(percent(Radiologist$Sens[3]), ", 95CI: (", percent(Radiologist$Sens_L[3]), " - ", percent(Radiologist$Sens_H[3]), ")")` and specificity of `r paste0(percent(Radiologist$Spec[3]), ", 95CI: (", percent(Radiologist$Spec_L[3]), " - ", percent(Radiologist$Spec_H[3]), ")")`.

Compared to the the human radiologists' grading encompassing any abnormality, the AI system demonstrated a statistically significant improvement in absolute specificity of 1.2% (95% confidence interval (CI) 0.29%, 2.1%; P = 0.0096 for superiority) and an improvement in absolute sensitivity of 2.7% (95% CI −3%, 8.5%; Extended Data Table 2a).

###  ROC Curves

![](Results/Figure-2 ROCs.tif){width=900px}
The ROC graph shows that regardless of the CAD4TB cut-off value selected, the software’s performance was inferior compared to the radiologist among all referral groups. The area under the curve (AUC) for all referral groups is 0.74 (95% CI: 0.73-0.75). The CAD4TB software performed significantly better among walk-ins (AUC 0.84, 95% CI: 0.81-0.87) compared to people referred from NTP facilities (AUC 0.77, 95% CI: 0.74-0.79) and private providers (AUC 0.72, 95% CI: 0.70-0.73).

###  Precision Recall Curve (Xpert Reference)

@@

@@

We observe that the performance of XXX PRODUCTS varies across age groups. We also find that all DL systems perform worse on XXX than on, which is consistent with the decreased sensitivity of radiologists for patients... Differences in the model’s performance in benign/not benign classification is larger than in malignant/not malignant classification. We hypothesize that this is due to age and prior TB hisotry there are more abnormality on the chest or old scaring influenced the detection of active TB.

>>>>

# Introduction
The improved theoretical understanding in AI technology, the ubiquity of large annotated datasets, and the advance in computer power have fostered a rapid expansion of the AI industry in medical diagnosis. Until recently, the most accurate AI methods for image analysis require feature manual segmentation of anatomic structures, detection or computation of specific features annotated by experts. The breakthrough in the ImageNet 2012 Challenges popularized the use of deep learning in neural networks to analyse medical images. Inspired by the human nervous system, neural networks are interconnected functions, each comprised of a weight and a bias coefficient. In deep learning, the networks are trained using large sets of known positive and negative data (ground truth) in multiple hidden layers. The networks “learn” by adjusting the weights and biases of the underlying functions based on the difference between predictions and ground, a process called back-propagation. The increased computational power makes it possible for a complex deep learning network to modify itself using a large training dataset so that the resulting trained algorithms can identify new and unseen data.

@@

# Methods
In this retrospective study, we used data consecutively from all adults (> 15 years) presented any of the three TB Screening Centres (SCs), which were established by icddr,b with funding from the Stop TB Partnership's TB REACH Initiative, between 15 May 2014 and 4 October 2016. The three SCs cover a vast network of more than 2,000 private providers and 133 NTP facilities across Dhaka. After providing informed consent, each participant was verbally screened for symptoms and received a posterior-anterior CXR using digital X-ray machines (Delft EZ DR X-ray) and was asked to submit a sputum sample for a free Xpert test. Xpert test was performed again if the initial test failed (invalid, error, or no result). The final Xpert results were used as the bacteriological evidence and the reference standard in this evaluation. A group of 3 Bangladeshi, board-certified radiologists (all with MD/MBSS degree in radiology and X,Y,Z years of experience??) read all of the CXR images remotely. The radiologists were blinded to all testing and clinical (and demographic data?? icddr,b please confirm) data and provided standard radiology reports and graded each CXR as follows (criteria to be attached): a. Highly Suggestive: including highly suggestive of TB only, b. Possibly TB: including abnormality highly suggestive of TB and possibly associated with TB, c. Any Abnormality: including abnormality highly suggestive of TB, possibly associated with TB and non-TB abnormality, d. Normal. Anyone who was unable or unwilling to acquire a CXR was referred to a nearby public-sector health facility.

Through the network and the database of innovators developed under the TB REACH initiatives and the Accelerator for Impact project at Stop TB Partnership, we identified and selected five DL systems, all have stable version control, to be included in this study: CAD4TB (v6), qXR (v2) developed by Qure.ai (India), Lunit INSIGHT for Chest Radiography (v4.7.2) developed by Lunit (South Korea), JF CXR-1 (v2) developed by JF Healthcare (China) and InferRead®DR (v2) by Infervision (China). The 5 DL systems scored the images remotely through Secured File Transfer Protocol from the Stop TB repository except for Delft, in which case the data was shared through cloud transfer. All machine reading was performed independently with the developers blinded to all testing, clinical and demographic data. All DL systems produce a continuous abnormality score (from 0 to 100 or from 0% to 100%) presenting the probability of presence of TB. We assess the 5 DL systems firstly by describing the distribution of AI scores disaggregated by Xpert status and by prior history of TB. Mann-Whitney U test was used to compared non-normal distribution.

Instead of depending on the pre-defined threshold scored selected by some vendors, we choose the threshold cutoff to be comparative to the three categories used by the human readers (reading criteria described below). For example, for highly suggestive of TB, we chose the cutoff score to produce the same dichotomized screening decisions in terms of sensitivity and we compare the difference in specificity using McNemar test for paired proportions.

@@

A total of 24,031 people were consecutively recruited from the three TB SCs. Excluding 17 individuals without a CXR and 107 individuals aged 15 or less, a total of `r sum(MDF$Age>=15)`  individuals were included in this analysis. The median age was `r T1$Overall[2]`, and `r paste0(substr(as.character(T1$Overall[[3]]), 13,16), "%")` were female, and almost all (`r paste0(substr(as.character(T1$Overall[[9]]), 8,11), "%")`) had at least one TB-related symptom. The most common symptoms are cough (`r paste0(substr(as.character(T1$Overall[[4]]), 8,11), "%")`), fever (`r paste0(substr(as.character(T1$Overall[[5]]), 8,11), "%")`), weight loss  (`r paste0(substr(as.character(T1$Overall[[7]]), 8,11), "%")`), and shorteness of breath (`r paste0(substr(as.character(T1$Overall[[6]]), 8,11), "%")`). Hemoptysis was only reported in `r paste0(substr(as.character(T1$Overall[[8]]), 8,11), "%")` participants. Noticeably, there were `r paste0(substr(as.character(T1$Overall[[10]]), 7,10), "%")` participants suspected of having TB already had prior TB history. The prevalence of bacteriologically-confirmed (Bac+) TB, confirmed by Xpert, in this population overall was `r paste0(substr(as.character(T1$Overall[[11]]), 7,10), "%")`. Among Bac+ individuals, `r percent(sum(MDF$RIF.Result %in% "Detected")/sum(MDF$Xpert2Outcome_num %in% "1"))` were resistant to rifampicin. The radiologists graded `r T1$Overall[25]` as Highly Suggestive, `r T1$Overall[26]` as Possibly TB, `r T1$Overall[27]` as Any Abnormality. The medians of the abnormality scores in Bac+ group were significantly different from those in the Xpert negative group were (Mann-Whitney U test <0.05) for all 5 DL systems.

There are three sources of patients: the greatest proportion of test results came from people who were referred by either public sector or private sector health providers (n=`r T1$Overall[22]`);  `r T1$Overall[23]` individuals were tested in NTP DOTS facilities after an inital negative smear; and `r T1$Overall[24]` individuals walked-in / self-presented (Table 1). Across all referral groups,  `r T1$Overall[11]` MTB-positive TB patients were detected; the prevalence of Xpert positive TB was lowest among walk-ins: `r T1$WalkIn[11]`, highest in the NTP DOTS retested subgroup (`r T1[6, 11]`).

### Histogram 
![](Results/density.tif){width=900px}

The stacked density plot in Fig-X shows the distributions of the 5 DL systems' scores disaggregated by Xpert outcomes and by prior TB history. The dark and light red bars were Bac negative and the dark and light green bars were Bac positive. An ideal test should have a density plot with all the red bars left skewed (positive skew) and all green bars right skewed with no overlap. Lunit's, qXR's and InferReadDR's density plot showed the dichomization pattern. Although almost all Bac positive patients received high abnormality scores (95-100) from JF CXR-1, so were many Bac negative patients, of which, mostly were healthy people but with a prior TB history (dark red), leading to excessive recall. When separately examine the distribution of the abnormality scores from the health people but with priro TB history, the distrbutions of all DL systems were right skewed, instead of left skewed (InferReadDR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 33]),3)`,  qXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 28]),3)`, Lunit INSIGHT CXR: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 29]),3)`, CAD4TB: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 27]),3)`, and JF CXR-1: `r round(skewness(MDF[MDF$Xpert2Outcome_num ==0 & MDF$TB.Medication.History %in% "Yes", 30]),3)`), which we postulated resulted from issues in the algorithms' ability to differentiate between old scarrings and active lesions.

### Comparison of sensitivity and specificity between human reading and the predictions of the DL systems
```{r}
source("radiologist.R")
humanAI <- read.csv("Results/HumanAI.csv", )
knitr::kable(humanAI, row.names = F)
```

To compare the DL systems withthe group of Bangladeshi radiologists, we choose thresholds to match the sensitivity of each grading made by the human readers. The grading of "highly suggestive of TB" had a low sensitivity of `r paste0(percent(Radiologist$Sens[1]), " (95%CI: ", percent(Radiologist$Sens_L[1]), " - ", percent(Radiologist$Sens_H[1]),")")` but a high specificity of `r paste0(percent(Radiologist$Spec[1]), " (95%CI: ", percent(Radiologist$Spec_L[1]), " - ", percent(Radiologist$Spec_H[1]),")")`. All 5 DL systems demonstrated statistically significant improvement in specificity. The increases in specificities range from 1.48% (CAD4TB) to 8.96% (Lunit INSIGHT CXR).

If radiologists' rading of "Possibly TB" had been used to triage the follow-on Xpert testing, the resulting sensitivity would be `r paste0(percent(Radiologist$Sens[2]), " (95%CI: ", percent(Radiologist$Sens_L[2]), " - ", percent(Radiologist$Sens_H[2]), ")")` and the specificity would be `r paste0(percent(Radiologist$Spec[2]), " (95%CI: ", percent(Radiologist$Spec_L[2]), " - ", percent(Radiologist$Spec_H[2]), ")")`. The matching AI classificiation by the 5 DL systems continued showing statistical improvement in specificty. The increases in specificities range from 1.34% (JF CXR-1) to 7.62% (Lunit INSIGHT CXR).

The grading of "any abnormality" has high sensitivity, `r paste0(percent(Radiologist$Sens[3]), " (95%CI: ", percent(Radiologist$Sens_L[3]), " - ", percent(Radiologist$Sens_H[3]), ")")`, but a reduced specificity, `r paste0(percent(Radiologist$Spec[3]), " (95%CI: ", percent(Radiologist$Spec_L[3]), " - ", percent(Radiologist$Spec_H[3]), ")")`. The matching AI classification statistically outperform in terms of specificity. qXR gained the highest in specificity (`r paste0(humanAI$Diff.specificity[12], " (95%CI: ", humanAI$CI[12], ")")`).

###  Overall performance of 5 DL products

![](Results/Figure-2 ROCs.tif){width=900px}
We summarized the ROC curves by computing the area under the curve (AUC).

The area under the curve (AUC) for all referral groups is 0.74 (95% CI: 0.73-0.75). The CAD4TB software performed significantly better among walk-ins (AUC 0.84, 95% CI: 0.81-0.87) compared to people referred from NTP facilities (AUC 0.77, 95% CI: 0.74-0.79) and private providers (AUC 0.72, 95% CI: 0.70-0.73).

To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.

###  Threthold Selection

@@

To rule out normal cases with high confidence, we used a very-low decision threshold. For the UK data, we achieved a negative predictive value (NPV) of 99.99% while retaining a specificity of 41.15%.

@@

We compared that the performance of 5 DL systems varies across age groups. We also find that all DL systems perform worse on XXX than on, which is consistent with the decreased sensitivity of radiologists for patients... Differences in the model’s performance in benign/not benign classification is larger than in malignant/not malignant classification. We hypothesize that this is due to age and prior TB hisotry there are more abnormality on the chest or old scaring influenced the detection of active TB.

# Discussion

The study show that the 5 DL prdocuts had clinical potential. The classificaitions made by the DL system coul be used to when skilled radiologists are scare in high TB burden countries which improve the standard of care. The AI system could also be used to provide automated, immediate feedback in the screening setting.
